Class-based network segregation, Economic Inequality and Redistributive Preferences across societies

### 2024-02-04 paper1_jiturra.Rmd
up

---
title: "Class-based network segregation, Economic Inequality and Redistributive Preferences across societies"
css: "input/css/custom.css" # custom CSS para html
fontsize: 11pt
linestretch: '1.5'          # interlineado 
papersize: a4
link-citations: yes         # citas linkeadas
# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
date: "`r format(Sys.Date(), '%d %B %Y')`"
author:
- name: Julio Iturra-Sanhueza
#   affiliation: University of Bremen
#   email: jiturra@uni-bremen.de
#   number: 1
# - name: Justin d'Ottawa
#   affiliation: University of Ottawa
#   number: 2
# - name: Pedro Torres
#   number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
# abstract: |
#  The escalating economic inequality and the current sanitary crisis have threatened social cohesion among citizens. However, these consequences have been unevenly experienced across the social structure. The upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience. Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalisation and increasing the demand for welfare support. Particularly, social resources through network ties have been suggested to have a direct link with an individual’s welfare through instrumental and expressive outcomes, such as providing information or help in moments of need. Consequently, inequalities in access to certain social positions (i.e. occupations) are translated into a lack of social resources beyond individual economic and cultural capital. Additionally, it has been argued that social isolation not only plays a role in terms of resources but given that higher levels of segregation can bolster opinions, it is argued that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes. Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties. To addresss this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties. The results of multilevel estimations show that being socially segregated increases demand for redistribution. Additionally, this influence is conditional to social class, where the working and intermediate classes with highly homogeneous networks demand more governmental redistribution than the upper class. At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesised that income inequality could bolster the influence of social segregation on the demand for redistribution. However, cross-level interactions do not provide supporting evidence on this behalf. 
#    **Keywords**: network segregation, redistributive preferences, economic inequality 
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    number_sections: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
  bookdown::html_document2:
    toc: yes
    code_folding: hide
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false

always_allow_html: true      
linkcolor: blue                         # enlaces y citas en color azul
bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
csl: input/bib/apa6.csl
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \setlength\parindent{24pt} 
---

@@

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_minimal())
ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
```

# Class-based mechanism on attitudes toward economic inequality and welfare

key concepts: material interests, normative motivations, within-class differences,

The link between social class and political attitudes constitutes one of the most significant findings in sociology. The conceptual basis of these studies lies in the organization of classes as social barriers delineated mainly by ownership of the means of production, autonomy over one's work, and control over the work of others [@Erikson1992]. This perspective has been adopted from research on social mobility, focusing on occupations and their contractual status as fundamental characteristics to distinguish social classes [@ishida_trends_2005;@hertel_relation_2019]. Besides the literature on stratification and mobility, classes also trace distinctions in other domains of social life concerning voting behavior [@mainwaring_left_2015;@evans_decline_1993], cultural preferences [@Chan2007], and political attitudes [@Svallfors2006]. Regarding the latter, according to @lindh_class_2020, research on the link between class position and political attitudes has developed more extensively regarding the economic domain, addressing the economic interests of classes with an emphasis on redistribution, social security, and the social service functions of the welfare state (p. 421). In addition, the study of attitudes has been highlighted in the sociocultural domain, including people's views on issues such as gender relations, race and ethnicity, environmentalism, and sexuality (p. 425), as well as in the political domain concerning the capacity of political institutions to respond to the demands of the citizenry. Consequently, two main competing mechanisms that have linked class to attitudes in the economic domain can be mentioned. On the one hand, into those linked to material-self interests, and on the other hand, the mechanisms associated with normative motivations and values.

First, the self-interest mechanism has functioned as a canonical model to explain redistributive preferences, where the material interests of those with the most to gain from redistribution conflict with those in positions of greater material well-being [@meltzer_rational_1981]. Similarly, an extension of the model has incorporated the dimension of economic risk (e.g., unemployment), paying attention to occupations as the unit that conveys it; consequently, positions with greater exposure to risk would tend to be more in favor of measures that mitigate labor market risks [@rehm_risks_2009]. Second, part of the literature on Western societies has highlighted the cognitive dimension in preference formation. On the one hand, it is suggested that people with limited material resources oppose redistributive measures due to the inability to successfully link their condition with the redistributive outcome because of a lack of information, distorting their views on fairness and misaligning their material interests from their preferences [@bartels_homer_2005;@hvidberg_social_2020]. On the other hand, part of the literature has paid more attention to high-income groups, suggesting that they are far from being monolithic towards inequality when expressing their preferences towards redistribution, arguing that although the rational interest model maintains its general implications, there are nuances within these groups regarding perceived negative externalities that inequality could have at a general level, which would ultimately motivate altruistic support towards redistribution [@rueda_who_2019,@dimick_models_2018].

Material interests and normative orientations can be comprehended as competing mechanisms in preference formation. For example, basic human values such as self-transcendence, characterized by the pursuit of equality and concern for others [@Kulin2013], or humanitarianism, which puts human dignity at the center [@feldman_humanitarian_2001], would be linked to altruistic motivations and might ultimately explain egalitarian economic preferences. However, this link may be weakened according to the exposure to risk and the possession of resources, becoming more salient under conditions of greater security against market risks and material prosperity, such as those experienced by the upper classes, and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019]. In a similar vein, class differences in skills and work logic might influence normative orientations that are ultimately expressed in political attitudes and behavior, being particularly salient among the professional class [@oesch_redrawing_2006]. Thus, the time that workers spend in their workplace, as well as the social interactions embedded in it, is argued that the work logic operates as a socialization agent according to the type of performed task, where those in interpersonal services tend to be more supportive of progressive political views than those in technical and managerial positions [@oesch_electoral_2018; @edlund_influence_2003]. However, related research has recently suggested that it is indeed challenging to disentangle whether work logic operates as a socialization agent, where reverse causality should be considered given that early-life socialization in the family context might motivate self-selection processes into specific career paths, or alternatively, decisions in the organizational hiring logic have to be taken into account considering that certain profiles might be preferred for interpersonal or managerial positions [@langsaether_more_2020].

Critical views have argued that a disincentive of political attitude and behavior in relation to class position. The "death of class" thesis has argued that due to the increase of material welfare in post-industrial societies, the distributive struggle between classes has been waning, resulting in the salience of other group memberships, reorienting the political debate towards post-material issues [@clark_declining_1993;@inglehart_culture_1990]. Although the process of modernization has led to changes in citizens' concerns, it is feasible to argue that the distributive struggle between classes has not been completely displaced but cohabits with people's attitudes towards the position of women in society as well as their views on migration [@Svallfors2006]. As far as people's attitudes toward redistribution and the role of the state in providing social welfare are concerned, this thesis has suggested that class cleavage would lose relevance as the material welfare of society increases. However, the claimed blurring of the class cleavage has not had particularly strong empirical support in terms of people's preferences around the economic domain.

	[Evidence on class and political attitudes]
# Network segregation and social class	
While previous research has focused more extensively on the economic dimension of social class, such as employment relations and occupation, patterns of social interactions are also a constituent dimension of how classes shape their political views toward economic inequality. Given that social classes are defined in terms of property, authority, and power, they can be understood as fundamentally relational. Therefore, it would be arguable that class positions are not merely distinguished by the labor market position, authority, and control over labor but are also relationally defined based on their patterns of sociability. Hereby, the scope of class analysis in the formation of attitudes and behavior can be extended further to the individual and household situation, stressing the role of social interactions and network segregation processes that might influence the internalization of shared norms, identity formation, and conflict between classes.

For stratification scholars, the study of segregation relates to the inequality in the distribution of status position and group membership heterogeneity as the observable patterns of association that shape interpersonal ties often referred to as relational networks [@blau_inequality_1977]. Indeed, one of the most significant findings on network research is the stronger contact frequency and tie formation between individuals of similar characteristics described as homophily [@mcpherson_birds_2001; @lazarsfeld_friendship_1954], demonstrating that associations are segregated according to the degree of demographic availability of social groups, as well as by status differentiation that intersect group membership [@bargsted_pautas_2020; @plaza_juntos_2022]. However, it has been argued that segregation is also affected by sociopsychological factors, where in-group dynamics tend to be reinforced when attitudes and behavior are concentrated in isolated social environments, decreasing the chances of interchange of world views and opinions [@visser_attitudes_2004; @diprete_segregation_2011]. Nonetheless, besides the importance of socialization preferences, it has been argued that the distribution of status positions and group diversity tend to be more dominant in structuring social activities that provide opportunities for opportunity for contact and consolidation of social networks [@feld_focused_1981; @mcpherson_network_2019]. As for social classes, it could be argued that classes represent social differentiation insofar as they not only consider differences in status resources but also comprise patterns of sociability so that segregation can also be observed in terms of the distribution of social ties regarding class positions.

How classes are formed also provides insights regarding their social relations and sociability practices.  In sociology,  classes are understood as the common basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978]. According to habitus theory, classes seek to improve and maintain their position by stressing the importance of intergenerational transmission of resources, which is accomplished through the reproduction of socialization patterns and lifestyles expressed in tie formation between groups of similar status when it comes to partner and friendship choices, arguing that class *habitus* entails a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984]. Symbolic resources such as skills and education credentials serve to reinforce status distinctions between upper and lower classes, granting access to socially segregated environments and increasing the likelihood of reproducing privileged positions at the expense of lower classes [@bourdieu_reproduccion_1981]. Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992]. Altogether, these processes further reinforce social distinctions between classes and contribute to the persistence of class structures. Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes. Access to social resources embedded in social networks follows a pattern of accumulation that reproduces pre-existing inequalities, in which class positions are vital in accounting for mechanisms of exclusion and segregation across the class structure.

@@

Theoretically, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to vertically represent social resources embedded in social networks [@lin_social_2007]. Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_macrosociological_1977]. Therefore, _homogeneity_  is described as the lack of cross-class network ties. It is indeed conceptually more proximate to the homophily principle because it is anchored in ego’s class position. At the same time, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to a certain group that does not necessarily count with a reference position to describe the network composition. Hence, both approaches provide a set of alternatives for the study of social class from a network perspective that has been increasingly discussed in the stratification literature as well as in the scholarly discussion about social class and political attitudes.

# Class boundaries and political attitudes

>>>>

---
title: "Class-based network segregation, Economic Inequality and Redistributive Preferences across societies"
css: "input/css/custom.css" # custom CSS para html
fontsize: 12pt
linestretch: '1.15'          # interlineado 
papersize: a4
link-citations: yes         # citas linkeadas
lang: en-US
# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
date: "`r format(Sys.Date(), '%d %b %Y')`"
author:
- name: Julio Iturra-Sanhueza
#   affiliation: University of Bremen
#   email: jiturra@uni-bremen.de
#   number: 1
# - name: Justin d'Ottawa
#   affiliation: University of Ottawa
#   number: 2
# - name: Pedro Torres
#   number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
# abstract: |
#  The escalating economic inequality and the current sanitary crisis have threatened social cohesion among citizens. However, these consequences have been unevenly experienced across the social structure. The upper and intermediate classes, benefiting from privileged access to social resources, have shown resilience. Conversely, working-class families have faced deteriorating material conditions, leading to a heightened sense of marginalisation and increasing the demand for welfare support. Particularly, social resources through network ties have been suggested to have a direct link with an individual’s welfare through instrumental and expressive outcomes, such as providing information or help in moments of need. Consequently, inequalities in access to certain social positions (i.e. occupations) are translated into a lack of social resources beyond individual economic and cultural capital. Additionally, it has been argued that social isolation not only plays a role in terms of resources but given that higher levels of segregation can bolster opinions, it is argued that being isolated from other social classes can polarise attitudes mainly in the working and upper-middle classes. Employing data from the International Social Survey Programme - Social Networks  this research aims to understand to what extent the demand for redistribution is linked to social ties. To addresss this, ego-centred social networks are used to represent the degree of class-based homogeneity of social ties. The results of multilevel estimations show that being socially segregated increases demand for redistribution. Additionally, this influence is conditional to social class, where the working and intermediate classes with highly homogeneous networks demand more governmental redistribution than the upper class. At the macro level, as the current distribution of economic resources influences the opportunity structure, it has been hypothesised that income inequality could bolster the influence of social segregation on the demand for redistribution. However, cross-level interactions do not provide supporting evidence on this behalf. 
#    **Keywords**: network segregation, redistributive preferences, economic inequality 
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    number_sections: true
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
  bookdown::html_document2:
    toc: yes
    code_folding: hide
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false

always_allow_html: true      
linkcolor: black                         # enlaces y citas en color azul
bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
csl: input/bib/apa6.csl
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \setlength\parindent{24pt} 
---

@@

# Introduction

[~500 words]

# Theoretical views on class, social networks, and redistributive preferences

[~3000 words]

## Class divide in the economic domain

The link between social class and political attitudes constitutes one of the most relevant findings in sociology. Theoretically, studies in the social mobility field have defined classes as structural positions given their difference in labor market situations distinguished by employment relations, skills level, and authority within the workplace, which traditionally has been represented by occupations instead of relative income or educational credentials [@Erikson1992;@Erikson1979]. Besides the social stratification studies, political sociologists have systematically demonstrated that classes trace distinctions in other domains of social life as well, including ideological preferences [@evans_decline_1993], cultural consumption behavior [@Chan2007] and attitudes toward redistribution and welfare [@Svallfors2006]. Regarding the latter, during the last decades, the research on class and political attitudes has developed more extensively regarding the economic domain, addressing the economic interests of classes with an emphasis on redistribution, social security, and social service functions of the welfare state [@lindh_class_2020, p. 421].

Critical views have suggested that economic development and modernization have eroded the link between social class and political attitudes. Around the debate of the "death of class" thesis, it has been argued that due to the increase of material welfare in post-industrial societies, the distributive struggle between classes has been waning, resulting in the salience of other group identities as more relevant, reorienting the political debate towards post-material concerns [@clark_declining_1993;@inglehart_culture_1990]. However, although modernization has led to changes in citizens' concerns, it is feasible to argue that the distributive struggle between classes has not been wholly displaced but cohabits with people's attitudes in the sociocultural domain [@lindh_class_2020]. Empirically, the claimed blurring of the class cleavage has not been strongly supported, whereas class divides indeed shape attitudes in the economic domain in general, such as perceived class conflicts [@perez_class_2023;@edlund_democratic_2015], attitudes toward market-based inequality [@andersen_preferences_2018;@lindh_public_2015], and redistributive preferences in particular [@curtis_how_2015;@langsaether_more_2020;@brooks_why_2010]. In the broader context, scholars have identified two competing mechanisms to elucidate the relationship between social class and attitudes towards inequality, commonly referred to as the self-interest and normative value-driven motives perspectives.

Theoretically, self-interest has served as the canonical model to explain redistributive preferences, where the material interests of those with the most to gain from redistribution conflict with those in positions of greater material well-being [@meltzer_rational_1981]. Similarly, extensions of the model have paid more attention to occupation as a representation of potential unemployment risk, arguing that social classes with greater risk exposure are prone to support redistributive policies as they reduce labor market insecurity [@rehm_risks_2009]. Differently, part of the scholarly discussion has stressed the role of cognitive processes in preference formation for understanding why, even in contexts of greater economic disparities, the lower classes oppose redistributive policies, arguing that misinformation plays a crucial role in linking material conditions with the redistributive policies [@bartels_homer_2005;@druckman_preference_2000]. Similarly, it has been argued that contexts of greater segregation affect the inferences about social and economic inequality [@summers_deliberating_2022;@mijs_inequality_2018] that ultimately contribute to the decoupling of material interests from economic preferences [@hvidberg_social_2020;@garcia-castro_changing_2022].

As material interests might prevail in scarcity, normative or value-driven motivations emerge as an alternative explanation in preference formation when pure self-interest weakens. Thus, values such as self-transcendence or humanitarianism share a common spirit regarding their desire for equality and concern for human dignity, providing the common ground for altruism that ultimately motivates egalitarian preferences [@Kulin2013;@feldman_humanitarian_2001]. However, the protagonism of values is indeed conditioned to risk exposure and resource availability, becoming salient under conditions of greater security against market risks and material prosperity and weakening under conditions of greater vulnerability and material precariousness [@Maldonadoetal2019]. Related arguments have suggested that skills specificity and work logic represented in occupations play a role in forming political attitudes [@oesch_redrawing_2006]. Specifically, it is argued that the work logic, together with the performed tasks, socializes individuals given the time spent in their job as well as the provision of goods and services, suggesting that technical and managerial occupations hold more conservative political views compared to those performing interpersonal services [@oesch_electoral_2018]. However, it is challenging to disentangle if the class differences in attitudes are indeed explained through political socialization developed within workplaces because they might result from the internalization of social norms in early-life socialization that motivate self-selection into specific career paths or the organizational hiring logic requirements for interpersonal or managerial positions [@kitschelt_occupations_2014].

While prior research has predominantly concentrated on examining the impact of social class through an individualistic lens, it is noteworthy that more attention needs to be devoted to understanding the role of social environments in class relations. This omission is particularly surprising given that class positions are fundamentally rooted in production relations that make them inherently relational, not only in their economic underpinnings but also in the power dynamics entwined within class conflicts [@wright_comparative_1989]. Besides, the normative basis of class relations introduces the relevance of the dimensions of solidarity and reciprocity, which have been argued to provide the moral basis of the legitimacy and popular support for welfare schemes [@mau_moral_2003]. Hereby, we argue that the scope of class analysis in attitude formation urges to be extended further to the individual or household situation, stressing the role of social ties and segregation as part of the socialization processes involved in the internalization of shared norms, class identity formation, conflict, and cooperation between classes.

## Class relations and social networks

As social relations within the occupational structure serve as the foundation for class analysis, widening the examination to other dimensions of social life, such as family dynamics, the development of friendships, and diverse social activities, can significantly enrich the scope of class analysis, particularly concerning its relation to attitude formation. In this sense, social stratification scholars have paid attention to the intersection of status positions and group membership as the observable patterns of association referred to as relational networks [@blau_inequality_1977]. Empirically, homophily is one of the most significant findings in network research, whereas the likelihood of tie formation between individuals of similar characteristics is strong [@mcpherson_birds_2001; @lazarsfeld_friendship_1954], such as age and gender in tracing friendship and family ties, as well as the segregated social environments alongside ethnicity and socioeconomic status [@bargsted_pautas_2020; @plaza_juntos_2022]. In addition, psychosocial factors such as socialization preferences and group dynamics also play a role in segregation processes, considering that isolated social environments decrease the interchange of world views, reinforcing preferences towards in-group members and polarizing attitudes [@visser_attitudes_2004; @diprete_segregation_2011]. Nonetheless, without denying the relevance of socialization preferences, segregation has been predominantly explained through the lens of social differentiation in social activities that work as foci of contact opportunities that ultimately consolidate social networks [@feld_focused_1981; @mcpherson_network_2019]. From this scope, we argue that class positions consider differences in economic or cultural resources and patterns of sociability observed in the distribution of social ties.

How classes are formed also provides insights regarding their social relations and sociability practices. In sociology, classes are understood as the everyday basis for action, given their labor market situation, that ultimately shapes their access to opportunities and resources [@weber_economy_1978]. According to habitus theory, classes incur a series of distinctive practices pivoted in cultural capital as the basis for mutual recognition [@bourdieu_distinction_1984]. Thus, classes seek to improve their position through the intergenerational transmission of resources, whereas similarities in friendship and family choices play a crucial role in the reproduction privilege. Additionally, while symbolic resources reinforce status distinctions, access to exclusive social activities in the upper class increases segregation at the expense of excluding the lower classes [@bourdieu_reproduccion_1981]. Ultimately, classes consolidate their demographic and cultural identities by mobilizing resources and shared sociability practices, ensuring intergenerational reproduction of their structural positions [@goldthorpe_sobre_1992]. Altogether, these processes further reinforce social distinctions between classes and contribute to the persistence of class structures. Hence, the socialization of common lifestyles and shared worldviews facilitates the consolidation of social classes. Access to social resources embedded in social networks follows a pattern of accumulation that reproduces pre-existing inequalities, in which class positions are vital in accounting for mechanisms of exclusion and segregation across the class structure.

@@

Theoretically, these studies account for class-based network segregation as the degree of connectedness of an individual to different occupations is meant to vertically represent social resources embedded in social networks [@lin_social_2007]. Drawing on this approach, the attempts of stratification scholars have been focused on how social connections are distributed across the class structure as a matter of social integration [@blau_macrosociological_1977]. Therefore, _homogeneity_  is described as the lack of cross-class network ties. It is indeed conceptually more proximate to the homophily principle because it is anchored in ego’s class position. At the same time, _diversity_ is defined as the rate of dissimilar ties or simply the total ties to certain groups that do not necessarily count with a reference position to describe the network composition. Hence, both approaches provide a set of alternatives for the study of social class from a network perspective that has been increasingly discussed in the stratification literature as well as in the scholarly discussion about social class and political attitudes.

# Data, variables and method

[1500 words]

# Results

# Discussion and conclusion
